Service Chain Placement in SDNs\tnoteref{t1}

### 2019-03-13 src/chain.tex
fix lemma 1 + bib
elsarticle

%\nonstopmode
\documentclass[11pt]{article}
%\documentclass[runningheads]{llncs}

\usepackage{amsmath,amssymb,mathtools}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{xspace}
\usepackage{color,soul}
\usepackage{paralist}
\usepackage{stmaryrd}

% \usepackage[linesnumbered, ruled]{algorithm2e}

%\usepackage[final]{microtype}
\usepackage[final]{hyperref}
\usepackage{subfig}
%\usepackage{subcaption}

% FIX
\newcommand{\fix}[1]{{\color{purple}\textbf{#1}}}
% DEBUG
%\usepackage{lipsum}
%\usepackage{todonotes}
%\usepackage{lineno}
%\linenumbers

% EXTRA
%\usepackage{authblk}

@@

\renewcommand{\floatpagefraction}{0.6}

\parskip = \smallskipamount

\sloppy

%\spnewtheorem{observation}{Observation}{\bfseries}{\itshape}

@@

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

@@

\begin{document}

\title{\bf Service Chain Placement in SDNs%
\thanks{%
%
A preliminary version appeared in the 3rd International Workshop on
Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017.
%
Research supported in part by Network Programming (Neptune)
Consortium, Israel.}
%
}

%\titlerunning{Service Chain Placement in SDNs}

%\author[1]{Gilad Kutiel%
%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}

%\author[2]{Dror Rawitz%
%\thanks{Partially supported by the Israel Science Foundation
%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}

%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}

\author{%
Gilad Kutiel%
\thanks{Department of Computer Science, Technion, Haifa 32000, Israel.} \\
{\tt\small gkutiel@cs.technion.ac.il}
\and
Dror Rawitz%
\thanks{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel. Partially supported by the Israel Science Foundation
  (grant no.~497/14). } \\
{\tt\small dror.rawitz@biu.ac.il}
}

\begin{titlepage}

\maketitle

@@

\bigskip

\noindent
\textbf{Keyworks}:
approximation algorithms,
randomized algorithms,
network function virtualization,
resource allocation,
service chaining,
software defined network.

\renewcommand{\thepage}{}
\end{titlepage}
\pagenumbering{arabic}

@@

\begin{figure}[t]
\centering
\scalebox{0.9}{
\input{fig-embedding}
}
\caption{\fix{
  An example of an \scp instance and a solution.
  The left DAG represents the collection of alternative service chains as requested by the client.
  Each node of this graph represent a single service and the number written inside the node is the processing demand of this service.
  The value on the arcs are the minimum bandwidth required to transmit the output of one service to the next service.
  \\
  The right DAG represents a physical network. 
  The numbers on the nodes represent processing capacities and the number on the arcs represent the available bandwidth.
  \\
  The blue, dashed, arcs represent the chosen service chain and a physical route respectively, and the dotted, purple, arrows show a placement of this service chain into the physical route.
}}
\label{fig:solution}
\end{figure}

@@

\begin{figure}[t]
  \centering
\scalebox{1}{
  \input{fig-reduction}
}
\caption{The specification defined in the proof of Theorem~\ref{thm:simple}.}
\label{fig:simple}
\end{figure}

@@

\begin{figure}[t]
\centering
\scalebox{.75}{
\input{fig-reduction2}
}
\caption{A reduction from a partition instance $a_1, \ldots, a_n$.
  The cost function enforces each $\alpha_i$ to be placed either in
  $v_i^-$ or in $v_i^+$.  In the former case this placement incure no
  cost but additional latency of $a_i$, in the later case there will
  be additional $a_i$ cost with zero latency.}
\label{fig:reduction2}
\end{figure}

@@

\begin{lemma}
\label{lemma:guess}
$c(f') \leq (1+\eps)c(f)$.
\end{lemma}
\begin{proof}
We have that
\begin{align*}
c(f')
%&
=    \sum_{\alpha} c(\alpha,f'(\alpha)) %\\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f'(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot
     \sum_{\alpha}
       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max} + 1}} \\
%& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
& =    c(f) + \eps c_{\max} \\
& \leq (1+\eps) c(f)
~,
\end{align*}
where the second inequality is due to the optimality of $f'$ with
respect to $c'$.
\end{proof}

@@

\begin{theorem}
\label{thm:fptas}
There exists an FPTAS for \scp in DAGs.
\end{theorem}
\begin{proof}
Given $\eps>0$, run the dynamic programming algorithm from
Section~\ref{sub:DPL} $\abs{\calV} \cdot \abs{V}$ times, once for each
possible value of $c_{\max}$, and choose the best placement.
\fix{Since we check all the possible values of $c_max$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.  
The running time is polynomial in the input size and in $1/\eps$.
\end{proof}

@@

\bibliographystyle{abbrv}
\bibliography{chain}

\end{document}

>>>>

\nonstopmode
\documentclass[preprint,12pt]{elsarticle}

\usepackage{amsmath,amssymb,mathtools,amsthm}
% \usepackage{fullpage}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{stmaryrd}

\usepackage[final]{hyperref}
\usepackage{subfig}

@@

\journal{Discrete Applied Mathematics}

@@

% \newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

@@

% FIX
\newcommand{\fix}[1]{{\color{violet}\textbf{#1}}}

\begin{document}
\begin{frontmatter}

\title{Service Chain Placement in SDNs\tnoteref{t1}}
\tnotetext[t1]{
A preliminary version appeared in the 3rd International Workshop on
Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017.
%
Research supported in part by Network Programming (Neptune)
Consortium, Israel.
}

\author{Gilad Kutiel}
\ead{gkutiel@cs.technion.ac.il}
\address{Department of Computer Science, Technion, Haifa 32000, Israel.}

\author{Dror Rawitz\fnref{f1}}
\ead{dror.rawitz@biu.ac.il}
\address{Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.}
\fntext[f1]{Partially supported by the Israel Science Foundation (grant no.~497/14).}

@@

\begin{keyword}
approximation algorithms \sep randomized algorithms \sep network function virtualization \sep resource allocation \sep service chaining \sep software defined network.

\end{keyword}

\end{frontmatter}

@@

\begin{figure}[]
\centering
\scalebox{0.9}{
\input{fig-embedding}
}
\caption{\fix{
  An example of an \scp instance and a solution.
  The left DAG represents the collection of alternative service chains as requested by the client.
  Each node of this graph represent a single service and the number written inside the node is the processing demand of this service.
  The value on the arcs are the minimum bandwidth required to transmit the output of one service to the next service.
  \\
  The right DAG represents a physical network. 
  The numbers on the nodes represent processing capacities and the number on the arcs represent the available bandwidth.
  \\
  The blue, dashed, arcs represent the chosen service chain and a physical route respectively, and the dotted, purple, arrows show a placement of this service chain into the physical route.
}}
\label{fig:solution}
\end{figure}

@@

\begin{figure}[]
  \centering
\scalebox{1}{
  \input{fig-reduction}
}
\caption{The specification defined in the proof of Theorem~\ref{thm:simple}.}
\label{fig:simple}
\end{figure}

@@

\begin{figure}[]
\centering
\scalebox{.75}{
\input{fig-reduction2}
}
\caption{A reduction from a partition instance $a_1, \ldots, a_n$.
  The cost function enforces each $\alpha_i$ to be placed either in
  $v_i^-$ or in $v_i^+$.  In the former case this placement incure no
  cost but additional latency of $a_i$, in the later case there will
  be additional $a_i$ cost with zero latency.}
\label{fig:reduction2}
\end{figure}

@@

\begin{lemma}
\label{lemma:guess}
$c(f') \leq (1+\eps)c(f)$.
\end{lemma}
\begin{proof}
We have that
\begin{align*}
c(f')
%&
=    \sum_{\alpha} c(\alpha,f'(\alpha)) %\\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f'(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot \sum_{\alpha} c'(\alpha,f(\alpha)) \\
& \leq \frac{\eps c_{\max}}{n} \cdot
     \sum_{\alpha}
       \paren{ c(\alpha,f(\alpha)) \cdot \frac{n}{\eps c_{\max}} + 1} \\
%& =    c(f) + \frac{\eps c_{\max}}{n} \cdot n \\
& =    c(f) + \eps c_{\max} \\
& \leq (1+\eps) c(f)
~,
\end{align*}
where the second inequality is due to the optimality of $f'$ with
respect to $c'$.
\end{proof}

@@

\begin{theorem}
\label{thm:fptas}
There exists an FPTAS for \scp in DAGs.
\end{theorem}
\begin{proof}
Given $\eps>0$, run the dynamic programming algorithm from
Section~\ref{sub:DPL} $\abs{\calV} \cdot \abs{V}$ times, once for each
possible value of $c_{\max}$, and choose the best placement.
\fix{Since we check all the possible values of $c_{max}$ and for each such value we compute an optimal solution with respect to $c'$, then} according to Lemma~\ref{lemma:guess} the best placement is $(1+\eps)$-approximate.  
The running time is polynomial in the input size and in $1/\eps$.
\end{proof}

@@

\bibliographystyle{elsarticle-num} 
\bibliography{chain}
\end{document}
